Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-10-29 bbbq_article.tex
Add two immunopeptidomes studies, progress #229

%
% Figure 2
%
\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{bbbq_article_issue_157/results.png}
  \caption{
    \textbf{
      Robust prediction that TMH epitopes are presented \emph{in vivo}.
    }
    Bars show the percentage of peptides obtained from elution
    studies that is derived from a TMH, for MHC-I and -II,
    for two TMH prediction tools.
  }
  \label{fig:elution}
\end{figure}

>>>>

%
% Figure 2
%
\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{bbbq_article_issue_157/results.png}
  \caption{
    \textbf{
      Robust prediction that TMH epitopes are presented \emph{in vivo}.
    }
    Bars show the percentage of naturally ocurring peptides
    that are derived from a TMH. These percentages are shown for
    both MHC-I and -II (the columns), two sources of data (the
    rows) and two TMH prediction tools (the two bars). 
    IEDB = the Immune Epitope Database, non-IEDB = 
    \cite{schellens2015comprehensive} for MHC-I and
    \cite{bergseng2015different} for MHC-II.
  }
  \label{fig:elution}
\end{figure}
